---
title: "ChiSquare_Binary_1"
author: "Ziling Zeng"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## Perspective Understanding ##
```{r}
library(tidyverse)
df <- read.csv("/home/zzeng1/Innovation80/Innovation80/Perspective - Sheet1.csv")
```

```{r}
# Convert empty strings to NA
df[df == ""] <- NA

# Remove rows with missing values in "Perspective Understanding"
df_cleaned <- df %>% drop_na(Perspective.Understanding)

df_cleaned <- df_cleaned |> filter(Participant.Type == "Senior")

# Standardize the text format for categorical variables
df_cleaned$Perspective.Understanding <- tolower(trimws(df_cleaned$Perspective.Understanding))

# Create a contingency table
contingency_table <- table(df_cleaned$Survey.Type, df_cleaned$Perspective.Understanding)

# Perform the Chi-Square Test
chi_test <- chisq.test(contingency_table)

# Print results
print(chi_test)

# Display contingency table
print(contingency_table)
```

```{r}
# Relevel Survey.Type so "Pre" appears before "Post"
df_cleaned$Survey.Type <- factor(df_cleaned$Survey.Type, levels = c("Pre", "Post"))

# Create a summary table with proportions and standard error (SE)
summary_df <- df_cleaned %>%
  group_by(Survey.Type, Perspective.Understanding) %>%
  summarise(Count = n(), .groups = "drop") %>%
  mutate(SE = sqrt(Count))  # Approximate standard error for count data

# Create the bar plot with vertical error bars
ggplot(summary_df, aes(x = Survey.Type, y = Count, fill = Perspective.Understanding)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_errorbar(aes(ymin = Count - SE, ymax = Count + SE),
                position = position_dodge(width = 0.9), width = 0.2) +  # Adds vertical error bars
  labs(title = "Perspective Understanding by Survey Type",
       x = "Survey Type (Pre/Post)",
       y = "Count ± SE",
       fill = "Perspective Understanding") +
  theme_minimal()


```

## Distinterest in Interaction ##
```{r}
# Read the CSV file
interaction_data <- read.csv("/home/zzeng1/Innovation80/Innovation80/Interaction - Sheet1.csv",stringsAsFactors = FALSE)
# Convert empty strings to NA and remove them
interaction_data[interaction_data == ""] <- NA

interaction_data <- interaction_data %>% drop_na(Disinterest.in.Interaction)

# Exclude data from "Strands of Wisdom"
interaction_data <- interaction_data %>% filter(Participant.Type == "Senior")
# Create a contingency table
contingency_table <- table(interaction_data$Survey.Type, interaction_data$Disinterest.in.Interaction)

# Perform Chi-Square Test
chi_test <- chisq.test(contingency_table)

# Print results
print(chi_test)

# Display contingency table
print(contingency_table)

```
A Pearson’s chi-square test with Yates’ continuity correction was conducted to examine the relationship between survey time point (Pre vs. Post) and the perception that the younger person was uninterested in getting to know someone older. The results indicated a statistically significant association, X²(1, N = [sample size]) = 6.87, p = .009.

The significant result suggests that perceptions of younger individuals' disinterest in engaging with older individuals changed between the Pre and Post survey conditions. Specifically, participants were significantly less likely to perceive younger individuals as uninterested in getting to know older people in the Post survey compared to the Pre survey. This finding may indicate a positive shift in intergenerational engagement following the intervention. However, further research is needed to determine the extent and causes of this shift.
```{r}
# Relevel Survey.Type so "Pre" appears before "Post"
interaction_data$Survey.Type <- factor(interaction_data$Survey.Type, levels = c("Pre", "Post"))

# Create a summary table with proportions and standard error (SE)
summary_data <- interaction_data %>%
  group_by(Survey.Type, Disinterest.in.Interaction) %>%
  summarise(Count = n(), .groups = "drop") %>%
  mutate(SE = sqrt(Count))  # Approximate standard error for count data

# Create the bar plot with custom colors
ggplot(summary_data, aes(x = Survey.Type, y = Count, fill = Disinterest.in.Interaction)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_errorbar(aes(ymin = Count - SE, ymax = Count + SE),
                position = position_dodge(width = 0.9), width = 0.2) +  
  scale_fill_manual(values = c("Yes" = "#E69F00", "No" = "#56B4E9")) +  
  labs(title = "Disinterest in Interaction by Survey Type",
       x = "Survey Type (Pre/Post)",
       y = "Count ± SE",
       fill = "Disinterest in Interaction") +
  theme_minimal()

```
```{r}
# Read the dataset
inflexibility <- read.csv("/home/zzeng1/Innovation80/Innovation80/Inflexibility Perception - Sheet1.csv", stringsAsFactors = FALSE)

# Convert empty strings to NA and remove them
inflexibility[inflexibility == ""] <- NA
inflexibility <- inflexibility %>% drop_na(Inflexibility.Perception)  # Adjust column name as needed

# Debugging: Check column names
print(colnames(inflexibility))

# Ensure "Young" is correctly matched (trim spaces)
inflexibility$Participant.Type <- trimws(inflexibility$Participant.Type)

# Filter only Young participants
inflexibility <- inflexibility %>% filter(Participant.Type == "Young")

# Debug: Check if filtering removed all rows
print(nrow(inflexibility))
print(head(inflexibility))

# Create a contingency table
contingency_table <- table(inflexibility$Survey.Type, inflexibility$Inflexibility.Perception)

# Debug: Check if the table is empty
print(contingency_table)

if (nrow(contingency_table) == 0 | ncol(contingency_table) == 0) {
  print("Error: Contingency table is empty. Check column names and filtering.")
} else {
  # Perform Chi-Square Test
  chi_test <- chisq.test(contingency_table)
  
  # Print results
  print(chi_test)
}
```
```{r}
# Relevel Survey.Type so "Pre" appears before "Post"
inflexibility$Survey.Type <- factor(inflexibility$Survey.Type, levels = c("Pre", "Post"))

# Calculate counts for each category
summary_data <- inflexibility %>%
  group_by(Survey.Type, Inflexibility.Perception) %>%
  summarise(Count = n(), .groups = "drop")

# Calculate standard error
summary_data <- summary_data %>%
  group_by(Survey.Type) %>%
  mutate(Standard_Error = sqrt(Count))  # Approximation assuming Poisson distribution

# Plot the bar chart with error bars
ggplot(summary_data, aes(x = Survey.Type, y = Count, fill = Inflexibility.Perception)) +
  geom_bar(stat = "identity", position = position_dodge(), width = 0.6) +
  geom_errorbar(aes(ymin = Count - Standard_Error, ymax = Count + Standard_Error), 
                width = 0.2, position = position_dodge(0.6)) +
  labs(title = "Inflexibility Perception (Pre vs Post)",
       x = "Survey Type",
       y = "Count",
       fill = "Inflexibility Perception") +
  theme_minimal() +
  theme(text = element_text(size = 14))

```
```{r}
library(survey)  # Load the package
```
```{r}

# Calculate count of each group
group_counts <- inflexibility %>%
  group_by(Survey.Type, Inflexibility.Perception) %>%
  summarise(Count = n(), .groups = "drop")

# Calculate total sample size
total_count <- sum(group_counts$Count)

# Assign weight as the proportion of each group
group_counts <- group_counts %>%
  mutate(Weight = Count / total_count)

# Merge weight back into the original dataset (only keep relevant columns)
inflexibility <- inflexibility %>%
  select(Participant.Type, Program.Name, Survey.Type, Inflexibility.Perception) %>%
  left_join(group_counts, by = c("Survey.Type", "Inflexibility.Perception"))

# Debug: Print column names to check merge success
print(colnames(inflexibility))

# Ensure only one weight column exists
if ("Weight.x" %in% colnames(inflexibility)) {
  inflexibility <- inflexibility %>% rename(Weight = Weight.x)
} else if ("Weight.y" %in% colnames(inflexibility)) {
  inflexibility <- inflexibility %>% rename(Weight = Weight.y)
}

# Drop any extra columns from previous merges
inflexibility <- inflexibility %>% select(Participant.Type, Survey.Type, Inflexibility.Perception, Weight)

# Debug: Check dataset structure after fixing weight
print(head(inflexibility))

# Ensure 'Weight' is numeric
inflexibility$Weight <- as.numeric(inflexibility$Weight)

# Define survey design for weighting
design <- svydesign(ids = ~1, data = inflexibility, weights = ~Weight)

# Perform weighted chi-square test
weighted_chi_test <- svychisq(~Survey.Type + Inflexibility.Perception, design)

# Print results
print(weighted_chi_test)

```
```{r}
# Count "Yes" responses in each Survey.Type
yes_counts <- inflexibility %>%
  filter(Inflexibility.Perception == "Yes") %>%
  group_by(Survey.Type) %>%
  summarise(Yes_Count = sum(Weight), .groups = "drop")

# Count total responses in each Survey.Type
total_counts <- inflexibility %>%
  group_by(Survey.Type) %>%
  summarise(Total_Count = sum(Weight), .groups = "drop")

# Ensure the data is in the correct format
print(yes_counts)
print(total_counts)

# Run proportion test
prop_test <- prop.test(yes_counts$Yes_Count, total_counts$Total_Count)

# Print results
print(prop_test)

```
```{r}
# Read the dataset
understanding_data <- read.csv("/home/zzeng1/Innovation80/Innovation80/Understanding_Young - Sheet1.csv", stringsAsFactors = FALSE)

# Convert empty strings to NA and remove them
understanding_data[understanding_data == ""] <- NA
understanding_data <- understanding_data %>% drop_na(Understanding)

# Filter only Young participants
understanding_data <- understanding_data %>% filter(Participant.Type == "Young")

# Convert all "yes" to "Yes" before summarizing data
understanding_data <- understanding_data %>%
  mutate(Understanding = ifelse(Understanding == "yes", "Yes", Understanding))

# Verify the change
print(unique(understanding_data$Understanding))  # Ensure "yes" is gone

# Create a contingency table for Understanding (Pre vs Post)
contingency_table <- table(understanding_data$Survey.Type, understanding_data$Understanding)

print(contingency_table)

# Run chi-square test
chi_test <- chisq.test(contingency_table)

# Print results
print(chi_test)
```

```{r}
# Relevel Survey.Type so "Pre" appears before "Post"
understanding_data$Survey.Type <- factor(understanding_data$Survey.Type, levels = c("Pre", "Post"))

# Summarize counts for each group
summary_data <- understanding_data %>%
  group_by(Survey.Type, Understanding) %>%
  summarise(Count = n(), .groups = "drop")

# Calculate standard error (SE = sqrt(n), assuming Poisson distribution)
summary_data <- summary_data %>%
  group_by(Survey.Type) %>%
  mutate(Standard_Error = sqrt(Count))

# Verify that "yes" is gone before plotting
print(unique(summary_data$Understanding))

# Plot bar chart with error bars
ggplot(summary_data, aes(x = Survey.Type, y = Count, fill = Understanding)) +
  geom_bar(stat = "identity", position = position_dodge(), width = 0.6) +
  geom_errorbar(aes(ymin = Count - Standard_Error, ymax = Count + Standard_Error), 
                width = 0.2, position = position_dodge(0.6)) +
  labs(title = "Understanding (Pre vs Post) Among Young Participants",
       x = "Survey Type",
       y = "Count",
       fill = "Understanding") +
  theme_minimal() +
  theme(text = element_text(size = 14))


```
```{r}

# Read the dataset
disinterest_data <- read.csv("/home/zzeng1/Innovation80/Innovation80/Widom_Disint - Sheet1.csv", stringsAsFactors = FALSE)

# Convert empty strings to NA and remove them
disinterest_data[disinterest_data == ""] <- NA
disinterest_data <- disinterest_data %>% drop_na(Disinterest.in.Interaction)

# Create a contingency table comparing Young vs Senior
contingency_table <- table(disinterest_data$Participant.Type, disinterest_data$Disinterest.in.Interaction)

# Run chi-square test
chi_test <- chisq.test(contingency_table)

# Print results
print(chi_test)

```
```{r}
# Convert empty strings to NA and remove them
disinterest_data[disinterest_data == ""] <- NA
disinterest_data <- disinterest_data %>% drop_na(Disinterest.in.Interaction)

# Relevel Participant.Type so "Senior" appears before "Young"
disinterest_data$Participant.Type <- factor(disinterest_data$Participant.Type, levels = c("Young", "Senior"))

# Create a summary table with counts and standard error (SE)
summary_data <- disinterest_data %>%
  group_by(Participant.Type, Disinterest.in.Interaction) %>%
  summarise(Count = n(), .groups = "drop") %>%
  mutate(SE = sqrt(Count))  # Approximate standard error for count data

# Create the bar plot with error bars
ggplot(summary_data, aes(x = Participant.Type, y = Count, fill = Disinterest.in.Interaction)) +
  geom_bar(stat = "identity", position = position_dodge(), width = 0.6) +
  geom_errorbar(aes(ymin = Count - SE, ymax = Count + SE),
                width = 0.2, position = position_dodge(0.6)) +
  labs(title = "Disinterest in Interaction by Participant Type",
       x = "Participant Type",
       y = "Count ± SE",
       fill = "Disinterest in Interaction") +
  theme_minimal() +
  theme(text = element_text(size = 14))



```

```{r}

# Read the dataset
perspective_data <- read.csv("/home/zzeng1/Innovation80/Innovation80/Widom_Perspective - Sheet1.csv", stringsAsFactors = FALSE)

# Convert empty strings to NA and remove them
perspective_data[perspective_data == ""] <- NA
perspective_data <- perspective_data %>% drop_na(Perspective.Understanding)

# Create a contingency table comparing Pre vs Post
contingency_table <- table(perspective_data$Survey.Type, perspective_data$Perspective.Understanding)
print(contingency_table)
# Run chi-square test
chi_test <- chisq.test(contingency_table)

# Print results
print(chi_test)

```

```{r}
# Convert empty strings to NA and remove them
perspective_data[perspective_data == ""] <- NA
perspective_data <- perspective_data %>% drop_na(Perspective.Understanding)

# Relevel Survey.Type so "Pre" appears before "Post"
perspective_data$Survey.Type <- factor(perspective_data$Survey.Type, levels = c("Pre", "Post"))

# Create a summary table with counts and standard error (SE)
summary_data <- perspective_data %>%
  group_by(Survey.Type, Perspective.Understanding) %>%
  summarise(Count = n(), .groups = "drop") %>%
  mutate(SE = sqrt(Count))  # Approximate standard error for count data

# Create the bar plot with error bars
ggplot(summary_data, aes(x = Survey.Type, y = Count, fill = Perspective.Understanding)) +
  geom_bar(stat = "identity", position = position_dodge(), width = 0.6) +
  geom_errorbar(aes(ymin = Count - SE, ymax = Count + SE),
                width = 0.2, position = position_dodge(0.6)) +
  labs(title = "Perspective Understanding by Survey Type",
       x = "Survey Type (Pre/Post)",
       y = "Count ± SE",
       fill = "Perspective Understanding") +
  theme_minimal() +
  theme(text = element_text(size = 14))
```



