---
title: "Binary Data Analysis"
author: "Your Name"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_depth: 2
    number_sections: true
---

```{r}
library(tidyverse)
binarydata <- read.csv("/home/zzeng1/Innovation80/Innovation80/Binary Data - Sheet1.csv")
```

```{r}
colnames(binarydata)


# Convert columns to factors
binarydata$Participant.Type <- as.factor(binarydata$Participant.Type)
binarydata$Perspective.Understanding <- as.factor(binarydata$Perspective.Understanding)

# Remove empty values in Participant.Type
binarydata <- binarydata %>% filter(Participant.Type != "")

# Exclude programs without any data for Perspective Understanding
binarydata <- binarydata %>% group_by(Program.Name) %>% filter(any(!is.na(Perspective.Understanding))) %>% ungroup()

# Ensure factors are updated after removal
binarydata$Participant.Type <- factor(binarydata$Participant.Type)
# Create a contingency table
table_data <- table(binarydata$Participant.Type, binarydata$Perspective.Understanding)

# Run the Chi-square test
chi_square_result <- chisq.test(table_data)
print(chi_square_result)

# Check expected counts
chi_square_result$expected

```
```{r}
# Convert contingency table to data frame
data_table <- as.data.frame(table_data)
colnames(data_table) <- c("Participant_Type", "Perspective_Understanding", "Count")

# Calculate total counts for each participant type
total_counts <- binarydata %>% group_by(Participant.Type) %>% summarise(Total = n())
print(total_counts)

# Plot
plot <- ggplot(data_table, aes(x = Perspective_Understanding, y = Count, fill = Participant_Type)) +
  geom_bar(stat = "identity", position = "stack") +
  labs(title = "Perspective Understanding by Participant Type",
       x = "Perspective Understanding",
       y = "Count") +
  theme_minimal() +
  scale_fill_manual(values = c("blue", "orange"))

# Check unique values
unique(data_table$Participant_Type)

# Print plot
print(plot)



```

The results of the chi-square test indicate a significant association between participant type (senior vs. young) and responses to the survey item "unable to understand my perspective" (χ²(2) = 103.32, p < .001). The visualization suggests that young participants were more likely to select "No," indicating that they did not perceive others as unable to understand their perspective, whereas seniors had a more balanced distribution between "Yes" and "No" responses. Given the strong statistical significance, the differences observed are unlikely due to random chance and suggest meaningful distinctions in how seniors and young participants perceive perspective-taking in interactions. Further analysis, such as standardized residuals, could clarify which response categories contribute most to the observed association.
