---
title: "ChiSquare_Binary_1"
author: "Ziling Zeng"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
df <- read.csv("/home/zzeng1/Innovation80/Innovation80/Perspective - Sheet1.csv")
```

```{r}
# Convert empty strings to NA
df[df == ""] <- NA

# Remove rows with missing values in "Perspective Understanding"
df_cleaned <- df %>% drop_na(Perspective.Understanding)


# Standardize the text format for categorical variables
df_cleaned$Perspective.Understanding <- tolower(trimws(df_cleaned$Perspective.Understanding))

# Create a contingency table
contingency_table <- table(df_cleaned$Survey.Type, df_cleaned$Perspective.Understanding)

# Perform the Chi-Square Test
chi_test <- chisq.test(contingency_table)

# Print results
print(chi_test)

# Display contingency table
print(contingency_table)
```

```{r}
# Create a summary table with proportions and standard error (SE)
summary_df <- df_cleaned %>%
  group_by(Survey.Type, Perspective.Understanding) %>%
  summarise(Count = n(), .groups = "drop") %>%
  mutate(SE = sqrt(Count))  # Approximate standard error for count data

# Create the bar plot with vertical error bars
ggplot(summary_df, aes(x = Survey.Type, y = Count, fill = Perspective.Understanding)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_errorbar(aes(ymin = Count - SE, ymax = Count + SE),
                position = position_dodge(width = 0.9), width = 0.2) +  # Adds vertical error bars
  labs(title = "Perspective Understanding by Survey Type",
       x = "Survey Type (Pre/Post)",
       y = "Count ± SE",
       fill = "Perspective Understanding") +
  theme_minimal()

```
A Pearson’s chi-square test with Yates’ continuity correction was conducted to examine the relationship between survey time point (Pre vs. Post) and the perception that the other person had difficulty understanding. The results indicated a statistically significant association between survey time point and perceived difficulty in understanding, X²(1, N = 85) = 4.92, p = .027. The contingency table showed that in the Pre survey condition, 13 participants reported that the other person had difficulty understanding them, while 36 did not. In contrast, in the Post survey condition, only 2 participants reported difficulty, while 34 did not. These results suggest that after the intervention (Post survey), participants were significantly less likely to perceive that the other person had difficulty understanding them compared to the Pre survey condition, indicating a possible improvement in mutual understanding.

