---
title: "ChiSquare_Binary_1"
author: "Ziling Zeng"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## Perspective Understanding ##
```{r}
library(tidyverse)
df <- read.csv("/home/zzeng1/Innovation80/Innovation80/Perspective - Sheet1.csv")
```

```{r}
# Convert empty strings to NA
df[df == ""] <- NA

# Remove rows with missing values in "Perspective Understanding"
df_cleaned <- df %>% drop_na(Perspective.Understanding)

df_cleaned <- df_cleaned |> filter(Participant.Type == "Senior")

# Standardize the text format for categorical variables
df_cleaned$Perspective.Understanding <- tolower(trimws(df_cleaned$Perspective.Understanding))

# Create a contingency table
contingency_table <- table(df_cleaned$Survey.Type, df_cleaned$Perspective.Understanding)

# Perform the Chi-Square Test
chi_test <- chisq.test(contingency_table)

# Print results
print(chi_test)

# Display contingency table
print(contingency_table)
```

```{r}
# Create a summary table with proportions and standard error (SE)
summary_df <- df_cleaned %>%
  group_by(Survey.Type, Perspective.Understanding) %>%
  summarise(Count = n(), .groups = "drop") %>%
  mutate(SE = sqrt(Count))  # Approximate standard error for count data

# Create the bar plot with vertical error bars
ggplot(summary_df, aes(x = Survey.Type, y = Count, fill = Perspective.Understanding)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_errorbar(aes(ymin = Count - SE, ymax = Count + SE),
                position = position_dodge(width = 0.9), width = 0.2) +  # Adds vertical error bars
  labs(title = "Perspective Understanding by Survey Type",
       x = "Survey Type (Pre/Post)",
       y = "Count ± SE",
       fill = "Perspective Understanding") +
  theme_minimal()

```

## Distinterest in Interaction ##
```{r}
# Read the CSV file
interaction_data <- read.csv("/home/zzeng1/Innovation80/Innovation80/Interaction - Sheet1.csv",stringsAsFactors = FALSE)
# Convert empty strings to NA and remove them
interaction_data[interaction_data == ""] <- NA

interaction_data <- interaction_data %>% drop_na(Disinterest.in.Interaction)

# Exclude data from "Strands of Wisdom"
interaction_data <- interaction_data %>% filter(Participant.Type == "Senior")
# Create a contingency table
contingency_table <- table(interaction_data$Survey.Type, interaction_data$Disinterest.in.Interaction)

# Perform Chi-Square Test
chi_test <- chisq.test(contingency_table)

# Print results
print(chi_test)

# Display contingency table
print(contingency_table)

```
A Pearson’s chi-square test with Yates’ continuity correction was conducted to examine the relationship between survey time point (Pre vs. Post) and the perception that the younger person was uninterested in getting to know someone older. The results indicated a statistically significant association, X²(1, N = [sample size]) = 6.87, p = .009.

The significant result suggests that perceptions of younger individuals' disinterest in engaging with older individuals changed between the Pre and Post survey conditions. Specifically, participants were significantly less likely to perceive younger individuals as uninterested in getting to know older people in the Post survey compared to the Pre survey. This finding may indicate a positive shift in intergenerational engagement following the intervention. However, further research is needed to determine the extent and causes of this shift.
```{r}
# Create a summary table with proportions and standard error (SE)
summary_data <- interaction_data %>%
  group_by(Survey.Type, Disinterest.in.Interaction) %>%
  summarise(Count = n(), .groups = "drop") %>%
  mutate(SE = sqrt(Count))  # Approximate standard error for count data


# Create the bar plot with custom colors
ggplot(summary_data, aes(x = Survey.Type, y = Count, fill = Disinterest.in.Interaction)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_errorbar(aes(ymin = Count - SE, ymax = Count + SE),
                position = position_dodge(width = 0.9), width = 0.2) +  
  scale_fill_manual(values = c("Yes" = "#E69F00", "No" = "#56B4E9")) +  
  labs(title = "Disinterest in Interaction by Survey Type",
       x = "Survey Type (Pre/Post)",
       y = "Count ± SE",
       fill = "Disinterest in Interaction") +
  theme_minimal()
```

